---
title: "Econometrics with R"
author: "Benedikt Fritz & Marcel Schliebs"
date: "1 Februar 2018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
***
# Hello

Hi everyone from Benedikt and Marcel and welcome to this introductory **Applied Econometrics with R** tutorial. The following paragraphs shall get you familiar with R and hopefully make you full-fledged data scientists in no time. So let's get started. 

hier noch bisschen motivational stuff why R geil ist


***
# Technical Set-Up
***
## Installation

Hier Erklärung was was und links R-Studio + R download für windows und mac

***
## First Steps

Oberfläche erklären. Skript/Concole, usw. Evtl. screenshots

***
## Working Directories/PROJECTS

ordner erstellen mit projekt

***
## Packages

was sind packages (sammlungen von funktionen, wie installiere und lade ich blabla)



***
# taschenrechneR
***

***
### ```# lorem ipsum```
Comment. Everything behind a hashtag is not run by the program 

```{r}
1+1 #Hier habe ich eins und eins zusammengezählt
```	
  
***
### ```y <- x```  
Attribute x to y
```{r}
a <- "hello world"
a
```	


***

### ```x:y```  
Generates sequence of ganzzahlen
```{r}
1:3
```	

***

***
# R algebra

***
## Classes 

***
### Vectors

numeric,character,factor

***
### Matrices

***
### Data Frames

***
### Lists


***
## Indexing

### ```x[.]```  
Indexing of a vector 
```{r}
a <- c(1,2,3)
names(a) <- c("q","r","s")
a[1]
a[c(TRUE,TRUE,FALSE)]
a["s"]
```	

### ```x[.,.]```  
Indexing of data.frames (matix)	
```{r}
data(iris)
iris[1,1]
iris[1:2,1:2]
iris[1,]
```	

***
### ```$```
data(iris)
```{r}
data(iris)
table(iris$Species)
```	
***
### ```x == y; ; x != y ,x < y; x > y; x <= y; x >= y  ```	
Logical operators. Return TRUE/FALSE VALUES.
```{r}
1 == 2 #Gleichheit
2 != 3 #Ungleichheit
2 < 3 #Kleiner
2 <= 3 #Kleiner gleich
```	
vectorisation possible
***
```{r}
1 == c(1,2,3)
```	

### ```x %in% y```	
Checks which elements of vector x are included in y
```{r}
1:3 %in% 2:4
```	

***



***
# The tidyverse
Welcome to the tidyverse!

***

### ``` x %>% f(); x %<>% f() {magrittr}```	
The Pipe operator from the magrittr package pipes the last element of something into the first one of the next.  
```x %>% f()``` .
```{r}
library(magrittr)
mean(c(1,2,3,5))
c(1,2,3,5) %>% mean()
```	
... and  ```x %<>% f()``` pipes elements and overwrites in the end the initial object with the result of the calculations.
 ```{r}
a <- c(1,2,3)
a
a %<>% mean()
a
```	

***
### Mutate

***
### Summarise

***
### group_by

***

# Useful functions

### ```c()``` 
Combines elements to a vector
```{r}
c(1,2)
```



### ```read_spss(){haven}```
Read spss files via haven  (DIE HIER EHER DATAMANAGEMENT)
```
ess <- read_spss(file = "data/ESS7e02_1.sav",
                 user_na = TRUE)
```

***

### ```read_dta(){readstata13}``` 
Read dta files 
```
lala <- read_dta(file = "blabla",version = 13)
```

***

### ```within(data,{befehl})``` 
Execute r command within data environment. Returns modified dataset.```{}``` make sure that commands are executed across several lines.
```{r}
data(iris)
summary(iris$Sepal.Length)
iris <- within(iris,{
  Sepal.Length <- Sepal.Length + 10
})
summary(iris$Sepal.Length)
```

***

### ```table(x)``
***

### ```prop.table()```
***

### ```summary(x)```
***

### ```mean(x)```
***

### ```sum(x)```
***

### ```sd(x)```
***

### ```median(x)```

### ```round(2)```

### ```factor()```
